FinalManuscript_DISCS_UG

### 2018-10-08 parts/01_introduction_01contextofstudy.tex
[WIP] Numerical approximation section
Added work on numerical approximation, fixed appendix templates
Cleaned up some wording on Ch1

However, research has also considered homomorphic cryptosystems, which not only allow the secure transmission of data, but also allow computations with encrypted data. In a homomorphic cryptosystem, operations such as addition and multiplication can be performed on encrypted data. These operations are then preserved when the data is decrypted. In this manner, data is manipulated without compromising data privacy, as the encrypted data being operated on remains secure~\cite{fontaine_survey_2007, sen_homomorphic_2013}. While numerous homomorphic cryptosystems exist for use with digital data in general, in the area of homomorphic image encryption, there is additional interest in being able to perform image manipulation operations on the encrypted data such as image adjustment, filtering, and morphological/feature extraction operations~\cite{ziad_cryptoimg:_2016, gonzalez_digital_2008}.

>>>>

 In a homomorphic cryptosystem, operations such as addition and multiplication can be performed on encrypted data. These operations are then preserved when the data is decrypted. In this manner, data is manipulated without compromising data privacy, as the encrypted data being operated on remains secure~\cite{fontaine_survey_2007, sen_homomorphic_2013}. While numerous homomorphic cryptosystems exist for use with digital data in general, in the area of homomorphic image encryption, there is additional interest in being able to perform image manipulation operations on the encrypted data such as image adjustment, filtering, and morphological/feature extraction operations~\cite{ziad_cryptoimg:_2016, gonzalez_digital_2008}. More advanced operations have also been implemented using homomorphic cryptosystems, such as facial recognition \cite{hutchison_privacy-preserving_2009} and neural networks \cite{hesamifard_cryptodl:_2017}.

### 2018-10-08 parts/01_introduction_05scopeandlimitations.tex

We will implement and test the following algorithms:
\begin{enumerate}
	\item A variant of the Paillier cryptosystem~\cite{stern_public-key_1999} which supports floating-point operations, used in \textit{CryptoImg}~\cite{ziad_cryptoimg:_2016}.
	\item The Damgård-Geisler-Krøigaard (DGK) cryptosystem~\cite{pieprzyk_efficient_2007, cryptoeprint:2008:321} which is primarily used for secure integer comparison.
	\item A fully homomorphic encryption scheme by Dasgupta and Pal, which uses polynomial rings~\cite{dasgupta_design_2016}.
	\item The Brakerski-Gentry-Vaikuntanathan (BGV) cryptosystem \cite{cryptoeprint:2011:277}, an improvement on the lattice-based cryptosystem by Gentry~\cite{gentry_fully_2009}, with optimizations from Smart, Vercauteren and Halevi \cite{hutchison_fully_2010, cryptoeprint:2011:566}.
\end{enumerate}
We will implement and test the following categories of image manipulation operations:
\begin{enumerate}
	\item Non-linear image intensity adjustment (logarithm and power-log transformations)
	\item Facial detection and recognition using the eigenface approach \cite{turk_eigenfaces_1991}.
\end{enumerate}
We will adopt the benchmark for evaluating image quality of image encryption schemes presented by Ahmed, et. al~\cite{ahmed_benchmark_2016}. The presented benchmark reflects many tests used in other literature~\cite{ahmad_efficiency_2012, wu_npcr_2011}.
\begin{enumerate}
	%\item Tests for preservation of image quality after encryption and decryption
	%\begin{enumerate}
		\item Mean Squared Error (MSE)
		\item Peak Signal to Noise Ratio (PSNR)
		\item Structural Similarity Index (SSIM)
	%\end{enumerate}
	%\item Tests for cryptographic security
	%\begin{enumerate}
	%	\item Information entropy analysis
	%	\item Correlation coefficient analysis
	%	\item Differential analysis
  %      \begin{enumerate}
  %          \item Number of Pixel Change Rate (NPCR)
  %          \item Universal Average Change Intensity (UACI)
  %      \end{enumerate}
	%\end{enumerate}
\end{enumerate}
A detailed overview of the above will be provided in the methodology. Grayscale images will be used in the study.
A client-server model for secure computation will be assumed to allow operations such as secure comparison and exponentiation.

>>>>

We will implement and test the following algorithms:
\begin{enumerate}
	\item A variant of the Paillier cryptosystem~\cite{stern_public-key_1999} which supports floating-point operations, used in \textit{CryptoImg}~\cite{ziad_cryptoimg:_2016}.
    \item The Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK) cryptosystem~\cite{pieprzyk_efficient_2007, cryptoeprint:2008:321} which is primarily used for secure integer comparison.
	\item A fully homomorphic encryption scheme by Dasgupta and Pal, which uses polynomial rings~\cite{dasgupta_design_2016}.
	\item The Brakerski--Gentry--Vaikuntanathan (BGV) cryptosystem \cite{cryptoeprint:2011:277}, an improvement on the lattice-based cryptosystem by Gentry~\cite{gentry_fully_2009}, with optimizations from Smart, Vercauteren and Halevi \cite{hutchison_fully_2010, cryptoeprint:2011:566}.
\end{enumerate}
We will implement and test the following categories of image manipulation operations:
\begin{enumerate}
	\item Non-linear image intensity adjustment (logarithm and power-log transformations)
	\item Facial detection and recognition using the eigenface approach \cite{turk_eigenfaces_1991}.
\end{enumerate}
We will adopt the benchmark for evaluating image quality of image encryption schemes presented by Ahmed, et. al~\cite{ahmed_benchmark_2016}. The presented benchmark reflects many tests used in other literature~\cite{ahmad_efficiency_2012, wu_npcr_2011}.
\begin{enumerate}
	%\item Tests for preservation of image quality after encryption and decryption
	%\begin{enumerate}
		\item Mean Squared Error (MSE)
		\item Peak Signal to Noise Ratio (PSNR)
		\item Structural Similarity Index (SSIM)
	%\end{enumerate}
	%\item Tests for cryptographic security
	%\begin{enumerate}
	%	\item Information entropy analysis
	%	\item Correlation coefficient analysis
	%	\item Differential analysis
  %      \begin{enumerate}
  %          \item Number of Pixel Change Rate (NPCR)
  %          \item Universal Average Change Intensity (UACI)
  %      \end{enumerate}
	%\end{enumerate}
\end{enumerate}
A detailed overview of the above will be provided in the methodology. Grayscale images will be used in the study.
A client-server model for secure computation will be assumed to allow operations such as secure comparison and exponentiation.

### 2018-10-08 parts/02_relatedliterature.tex

We will now provide an overview of the \textit{CryptoImg} project, which our study is primarily based on. Then, we define the image processing operations we are interested in implementing in this study and
After establishing our desired image processing operations, introduce concepts in cryptography and define the four homomorphic cryptosystems we will be testing in the study.

>>>>

We will now provide an overview of the \textit{CryptoImg} project, which our study is primarily based on. Then, we define the specific image processing operations we are interested in implementing in this study. Then we will introduce concepts in cryptography and define the four homomorphic cryptosystems we will be testing in the study.

### 2018-10-08 parts/03_methodology_02nonlinearintensitytransformations.tex

\section{Non-Linear Intensity Transformations}
Aside from implementing the homomorphic encryption and decryption algorithms, we will also implement library functions for image negation, logarithm transformation and power-law transformation, as they are defined in~\cite{gonzalez_digital_2008}.
We now describe how we implement the logarithm and power-law image intensity transformations. In the case of partially homomorphic cryptosystems (Pailler, DGK), the following considerations will be made regarding required homomorphic operations not supported by the cryptosystems:
\begin{enumerate}
	\item If exponentiation is required, the secure exponentiation protocol in section \ref{ssec:exponentiationprotocol} will be used.
	\item If multiplication of ciphertexts $E(m_1), E(m_2)$ is required, the following protocol will be used:
	\begin{itemize}
		\item Bob calculates $E(m_1+m_2)$ and using the exponentiation protocol, acquires $E(m_1^2),E(m_2^2),E((m_1+m_2)^2)$.
		\item Bob can recover the product of the ciphertexts by computing
		\begin{align*}
			E((m_1+m_2)^2) - E(m_1^2) - E(m_2^2) = E(2m_1m_2),
		\end{align*}
		then carrying out the required constant multiplication to obtain $E(2m_1m_2)$.
	\end{itemize}
\end{enumerate}
\subsection{Logarithm Transformation}
The logarithm transformation of a pixel intensity value $x$ is defined as
\begin{align}
	T\left(x\right) = c \log\left(1 + x\right)
\end{align}
where $c$ is a constant.

>>>>

\section{Non-Linear Intensity Transformations}
Aside from implementing the homomorphic encryption and decryption algorithms, we will also implement library functions for image negation, logarithm transformation and power-law transformation, as they are defined in~\cite{gonzalez_digital_2008}.
We now describe how we implement the logarithm and power-law image intensity transformations. In the case of partially homomorphic cryptosystems (Paillier, DGK), if  exponentiation and multiplication is required, the secure protocols in section \ref{ssec:exponentiationprotocol} will be used.

\subsection{Logarithm Transformation}
The logarithm transformation of a pixel intensity value $x$ is defined as
\begin{align}
	T\left(x\right) = c \log\left(1 + x\right)
\end{align}
where $c$ is a constant.

### 2018-10-08 parts/08_appendices_a_cryptosystems.tex
RRL summary and fixes
- Commented out spatial filter section
- Updated summary to reflect new research
- Fixed some typesetting errors in D-P section

%\section{Sample Questions for Different Studies}
%The following table presents three sample studies, as well as the guide questions that may help direct the discussion in each section of the paper. You may use this as another reference in writing your paper.
\chapter{CORRECTION FOR DASGUPTA-PAL}
\label{ch:correction}
\section{Bitwise Description of the Dasgupta-Pal Cryptosystem}
The Dasgupta-Pal cryptosystem \cite{dasgupta_design_2016} encrypts each bit in a bit string independently.
In terms of the encryption of a single bit, the Dasgupta-Pal cryptosystem can be described as follows:
\begin{description}
	\item[Key generation]
	Let the secret key, $S_k$ be a large prime.
	Let the public refresh key, $R_k$, be $S_k \times z$, where $z$ is a large even integer.
	\item[Encryption]
	Given a message $m$, the encryption function is defined as
	\begin{align*}
		E(m) = m + S_kr
	\end{align*}
	where $r$ is a random integer.
	\item[Decryption]
	Given a ciphertext $c$, the decryption function is defined as
	\begin{align*}
		D(c) = c \bmod S_k \bmod 2
	\end{align*}
\end{description}
The homomorphic operations are then defined as
\begin{description}
	\item[XOR on ciphertexts]
	\begin{align*}
		D(E(a)+E(b)) = a \text{ XOR } b = (a + b) \bmod 2
	\end{align*}
	\item[AND on ciphertexts]
	\begin{align*}
		D(E(a)\times E(b)) = a \text{ AND } b = ab \bmod 2
	\end{align*}
\end{description}
After repeated operations on ciphertexts, the resulting ciphertext can grow in magnitude.
To prevent storage issues and keep the ciphertext size small, a refresh function is used.
\begin{description}
	\item[Refresh function]
	Given a ciphertext $c$, the refresh function is defined as
	\begin{align*}
		R(c) = c \bmod R_k
	\end{align*}
\end{description}
\section{Cases Where Decryption Fails}
We consider the following quantity:
\begin{align}
	\label{eq:cornercase_ciphertext}
	D(\underbrace{E(1)+E(1)+\cdots+E(1)}_{S_k \text{ times}}).
\end{align}
Since $S_k$ is odd, the corresponding operation in the plaintext space is
\begin{align*}
	\label{eq:cornercase_plaintext}
	\underbrace{1 \text{ XOR } 1 \text{ XOR } \cdots \text{ XOR } 1}_{S_k \text{ times}} = 1.
\end{align*}
However, evaluating Equation \ref{eq:cornercase_ciphertext} yields:
\begin{align*}
	D(\underbrace{E(1)+E(1)+\cdots+E(1)}_{S_k \text{ times}})
	&= D\left(\sum_{i=1}^{S_k}{(1+S_kr_i)}\right)\\
	&= D\left(S_k + S_k\sum_{i=1}^{S_k}{r_i}\right)\\
	&= \left(S_k + S_k\sum_{i=1}^{S_k}{r_i}\right) \bmod S_k \bmod 2\\
	&= 0 \bmod 2\\
	&= 0.
\end{align*}
Since $\underbrace{1 \text{ XOR } 1 \text{ XOR } \cdots \text{ XOR } 1}_{S_k \text{ times}} = 1\neq 0 = D(\underbrace{E(1)+E(1)+\cdots+E(1)}_{S_k \text{ times}})$, we have shown an instance where incorrect decryption occurs given a sequence of operations on ciphertexts.

>>>>

%\section{Sample Questions for Different Studies}
%The following table presents three sample studies, as well as the guide questions that may help direct the discussion in each section of the paper. You may use this as another reference in writing your paper.
\chapter{CORRECTION FOR DASGUPTA--PAL}
\label{chap:correction}
\section{Bitwise Description of the Dasgupta--Pal Cryptosystem}
The Dasgupta--Pal cryptosystem \cite{dasgupta_design_2016} encrypts each bit in a bit string independently.
In terms of the encryption of a single bit, the Dasgupta--Pal cryptosystem can be described as follows:
\begin{description}
	\item[Key generation]
	Let the secret key, $S_k$ be a large prime.
	Let the public refresh key, $R_k$, be $S_k \times z$, where $z$ is a large even integer.
	\item[Encryption]
	Given a message $m$, the encryption function is defined as
	\begin{align*}
		E(m) = m + S_kr
	\end{align*}
	where $r$ is a random integer.
	\item[Decryption]
	Given a ciphertext $c$, the decryption function is defined as
	\begin{align*}
		D(c) = c \bmod S_k \bmod 2
	\end{align*}
\end{description}
The homomorphic operations are then defined as
\begin{description}
	\item[XOR on ciphertexts]
	\begin{align*}
		D(E(a)+E(b)) = a \text{ XOR } b = (a + b) \bmod 2
	\end{align*}
	\item[AND on ciphertexts]
	\begin{align*}
		D(E(a)\times E(b)) = a \text{ AND } b = ab \bmod 2
	\end{align*}
\end{description}
After repeated operations on ciphertexts, the resulting ciphertext can grow in magnitude.
To prevent storage issues and keep the ciphertext size small, a refresh function is used.
\begin{description}
	\item[Refresh function]
	Given a ciphertext $c$, the refresh function is defined as
	\begin{align*}
		R(c) = c \bmod R_k
	\end{align*}
\end{description}
\section{Cases Where Decryption Fails}
We consider the following quantity:
\begin{align}
	\label{eq:cornercase_ciphertext}
	D(\underbrace{E(1)+E(1)+\cdots+E(1)}_{S_k \text{ times}}).
\end{align}
Since $S_k$ is odd, the corresponding operation in the plaintext space is
\begin{align*}
	\label{eq:cornercase_plaintext}
	\underbrace{1 \text{ XOR } 1 \text{ XOR } \cdots \text{ XOR } 1}_{S_k \text{ times}} = 1.
\end{align*}
However, evaluating Equation \ref{eq:cornercase_ciphertext} yields:
\begin{align*}
	D(\underbrace{E(1)+E(1)+\cdots+E(1)}_{S_k \text{ times}})
	&= D\left(\sum_{i=1}^{S_k}{(1+S_kr_i)}\right)\\
	&= D\left(S_k + S_k\sum_{i=1}^{S_k}{r_i}\right)\\
	&= \left(S_k + S_k\sum_{i=1}^{S_k}{r_i}\right) \bmod S_k \bmod 2\\
	&= 0 \bmod 2\\
	&= 0.
\end{align*}
Since $\underbrace{1 \text{ XOR } 1 \text{ XOR } \cdots \text{ XOR } 1}_{S_k \text{ times}} = 1\neq 0 = D(\underbrace{E(1)+E(1)+\cdots+E(1)}_{S_k \text{ times}})$, we have shown an instance where incorrect decryption occurs given a sequence of operations on ciphertexts.
